The limits of self commitment and private paternalism \thanks{}

### 2020-06-16 main.tex
Update of numbers in paper

@@

\title{The limits of self commitment and private paternalism \thanks{}}
\author{Joyce Sadka \and Enrique Seira \and Isaac Meza  \thanks{Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@itam.mx; Meza: University of California at Berkeley, isaac.meza@berkeley.edu} }
\date{This draft:  \today \\[2 cm]}

@@

We study the benefits of ``private paternalism'' in the understudied but important pawnbroker context. We show that forcing people into commitment contracts with financial penalties for not paying on time decreases their (fee-including) financial cost by \hlgr{11\%}, increases the likelihood of recovering their pawn by \hlgr{23\%}, and increases the likelihood of repeat business by \hlgr{20\%}. While virtually all clients would reduce their financing cost with the commitment contract, we show that only 10\% choose it. Using salient personal promises instead of pecuniary penalties as commitment triples contract take-of, but has not effect on financial costs or pawn recovery.

@@

\textbf{Keywords: } Private paternalism, choice, present bias, commitment, pawnshops.

\textbf{JEL codes:} XXX

@@

\cite{Laibson2018} recently noted that many institutions ---firms, schools, financial contracts--- restrict choice using built-in incentive/commitment mechanisms which help workers, students, borrowers overcome self-control problems. ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''. Similarly, mortgages do so ``with a fixed repayment stream and mandatory principal repayment''. However he notes that these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.} restrictions''. In this, he sees an important \textit{commitment puzzle}: if clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them. The fact that this is not the case suggests some clients may be naive about their self control problems, and that \textit{private paternalism}  ---a policy of restricting choice implemented by private firms--- may increase clients' welfare.

This paper studies private paternalism in the context of pawnbroker borrowing and finds evidence for its benefits. Pawnshops offer secure loans using items of personal property as collateral. The items pawned are called pledges or pawns. Pawn loans are one of the oldest forms of borrowing, and although data on their market share is scarce, anecdotal evidence suggests they are very prevalent. To give an example, our partner pawnshop (henceforth Lender $P$) served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were approximately 2.3 million micro-finance clients in Mexico in 2009 in Mexico (\cite{Pedroza:2010}). We cannot be more precise on the number of total borrowers from Lender $P$ for confidentiality reasons.}  Pawn loans are interesting to study in and on themselves for this reason alone. But they are also interesting because regulators and practitioners view pawnbrokers as the lenders to which people in desperate need turn to. The regulators' concern is that the selection of clients that go to pawnshops may be particularly vulnerable, have bad debt management skills, and are more likely to be present biased and naive about it.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients: \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.}

Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete. Conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn and their payment. In our survey 68\% report self-control problems in several domains.%, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and \hl{19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.

Consistent with little client sophistication, Lender $P$ offers a very simple but highly collateralized contract. It only accepted gold jewelry as collateral and approves all gold pawns, giving in exchange in cash the equivalent of 70\% of the weighted gold value. The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest. The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties. However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this). All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch. The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry. Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers. %This lets us focus more cleanly on behavioral economics aspects.

To study the benefits of private paternalism, we implemented a relatively large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying their monthly installment on time can actually decrease total fee-inclusive financing cost. Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice? Notice that any payment profile implemented in the commitment contract can be replicated under the status quo contract, but the later has more flexibility to respond to income shocks without incurring in fees. Third, what types of clients would demand these contracts that restrict choice? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? A large and important lab experiment literature suggest that promises change behavior significantly in laboratory settings, but we know little about their effect on the field in natural environments.\footnote{Some important papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.} Finally and importantly, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?

The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{Status-quo group}). The second arm (\textit{Fee-forced group}) was assigned into a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.

We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by \hlgr{11\%} on average, while the likelihood of recovering their pawn increases by \hlgr{19\%}. This is robust to including  transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings. The most economically vulnerable, those that report being stressed, and those that asked for a reminder at baseline, experience the largest financial cost savings. Those we classify as present biased and those that requested a reminder at baseline experience the largest effects on pawn recovery. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, we find that borrowers assigned to the forced fee-commitment contract are \hlgr{5pp} (\hlgr{20\%} of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.

@@

In spite of these estimated benefits for all clients, their actual demand for the fee-commitment contract is low. Only \hlgr{10\%} of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract. We had two assistants from the research team in each of the experiment's branches every day for all branch opening hours, material was developed to explain the differences among the two contracts, and subjects spelled back to assistants the loan differences. Furthermore take up is systematically predicted by baseline covarites\footnote{We find that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and ask for a remainder to payment (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice. The opposite holds for those that are more vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.}, making it less likely that it is just random mistakes. Low demand for commitment is consistent with most of the literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could we welfare improving for the naive. We estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery. These effects are zero throughout the quantile distribution.

@@

How much money is left on the table by the prevalence of the status-quo choice? We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \hlgr{\$300} pesos, close to 10\% of the average loan value. In particular \hlgr{95\%} of those that chose the status-quo contract would have been better in the fee-commitment contract, while only \hlgr{7\%} of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be welfare increasing for the overwhelming majority of clients.

Inspired by a significant lab experiment literature on the effects of promises on behavior, we also implemented a ``psychological commitment'' in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise. 
To do this we implemented two other treatment arms. A \textit{promise-forced} arm exactly analogous to our \textit{fee-forced arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise. Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise-forced} contract and the \textit{Status-quo} contract.

We document two main results in the promise arms. First, demand for the \textit{Promise-forced} contract is three times bigger than for the \textit{Fee-forced} contract, with \hlgr{31\%} take-up. This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view. Second, the \textit{Promise-forced} contract had zero effects on average and for an overwhelming fraction of the population on financing cost and pawn recovery. The same is true for the \textit{Promise-choice arm}. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior. Contrary to lab evidence, people did not keep the promise, at least the way it could be implemented in the field.\footnote{The government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but they rely on group lending, and therefore social collateral is at stake.}

@@

Pawn borrowing is one of the oldest form of borrowing and one to which people with little access to the formal credit market turn to for ``energency'' loans. They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}). In spite of this, there are extremely few studies in the economics literature about it. Why people go, how much it costs, what different contracts can tell us about consumer biases. We study such  context with Lender $P$, one of the largest pawn shops in Mexico, with \hl{several hundred} branches spanning multiple States in Mexico.

Lender $P$ was interested in understanding why half of their clients lost their pawn. It was concerned with high default rates for two reasons. The first is that the pawned piece may have a sentimental value to the client above of its gold value, making it inefficient for the lender to keep the piece. We actually find that clients report a subjective value that is almost \hlgr{twice} the value of its gold content. Second, it thought that keeping the piece lowered client satisfaction and made the client less likely to return and pawn again. They were interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract. Default is really  in this context  compared to many papers in the microfinance literature. \cite{Pande} study of the effect of payment frequency work in a context where the rate of default is close to 1\%. \cite{LittleAtAtime} has a baseline default of \hl{XX\%}.

One potential explanation for high default is that clients are really just selling their gold piece. This is unlikely for the large majority of people not only because the reported subjective value of the pawn is larger than the loan size for \hlgr{86\%} of them, but also because among that lose their pawn \hlgr{74\%} paid a positive amount towards its recovery. This can only be rationalized if they expected to recover their pawn.  Figure \ref{proxy_naive} focuses on those that ended up losing the pawn in our experiment and plots different measures of engagement with Lender $P$. Panel (c) shows total payments that went towards the loan. On average clients that lost their pawn paid \hlgr{34\%} of the value their loan. Panel (d) shows that while 40\% made zero payments, the rest made one or several payments. In fact, panel (b) shows that close to \hlgr{50\%} of clients extended the loan for another cycle and made payments in the second cycle.

@@

Lender $P$ had only one type of contract. It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime and no penalty for pre-payment. If the client paid the principal plus the accumulated interest before those 105 days, the she received back her pawn, otherwise the pawnbroker kept the piece and any payments done. Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms. The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.

This contract was standard in the industry, the clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn. Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history. Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below, even though \hlgr{90\%} of them have pawned before.

@@

We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece. The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others. We were able to survey \hlgr{7,703} clients (some refused). %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
\hlgr{The appendix transcribes the questionnaire in English and presents summary stats}. Survey response rate is 57\%, \hlgr{the Appendix Table} \ref{balance_response} shows that response is not related to admin data observables.

@@

\subsection{More on implementation.}

>>>>

\usepackage{comment}
\usepackage{subcaption,graphicx}

@@

\title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement. We want to thank also Ricardo Olivares for excellent research assistance and Erik Molina help with formatting. Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin and seminar participants at ITAM provided very valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@itam.mx; Meza: University of California at Berkeley, isaac.meza@berkeley.edu} }
\date{This draft:  \today \\[2 cm]}

@@

We study the benefits of ``private paternalism'' in the understudied but important pawnbroker context. We show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.5\%, increases the likelihood of recovering their pawn by 25\%, and increases the likelihood of repeat business by 55\%. Using the recent machine learning methods for estimating heterogeneous treatment effects, we calculate that more than 90\% clients would reduce their financing cost with the commitment contract, however 10\% choose it. Using personal promises instead of fees as commitment triples take-of but has no effects.

@@

\textbf{Keywords: } Private paternalism, choice, present bias, naivete, overconfidence, commitment, pawnshop.

\textbf{JEL codes:} G41, C93, O16, G21

@@

\cite{Laibson2018} recently noted that many institutions ---firms, schools, financial contracts--- restrict choice using built-in incentive/commitment mechanisms which help workers, students, borrowers overcome self-control problems. ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''. Similarly, mortgages do so ``with a fixed repayment stream and mandatory principal repayment''. However he notes that these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.} restrictions''. In this he sees an important \textit{commitment puzzle}: if clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them. The fact that this is not the case suggests some clients may be naive about their self control problems, and that \textit{private paternalism}  ---a policy of restricting choice implemented by private firms--- may increase clients' welfare.

This paper studies private paternalism in the context of pawnbroker borrowing and finds evidence for its benefits. Pawnshops offer secure loans using items of personal property as collateral. The items pawned are called pledges or pawns. Pawn loans are one of the oldest forms of borrowing, and although data on their market share is scarce, anecdotal evidence suggests they are very prevalent. To give an example, our partner pawnshop (henceforth Lender $P$) served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were approximately 2.3 million micro-finance clients in Mexico in 2009 in Mexico (\cite{Pedroza:2010}). We cannot be more precise on the number of total borrowers from Lender $P$ for confidentiality reasons.}  Pawn loans are interesting to study in and on themselves for this reason alone. But they are also interesting because regulators and practitioners view pawnbrokers as the lenders to which people in desperate need turn to. The regulators' concern is that the selection of clients that go to pawnshops may be particularly vulnerable, have bad debt management skills, and be more likely to have present biased preferences while being naive about it.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse. It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients. Congress has enacted laws in this regard. \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.}

Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 44\% of them do, suggesting naivete. Even conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn and their payment. In our survey 69\% report self-control problems saying they often fall into temptation spending. %, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and \hl{19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.

Consistent with little client sophistication, Lender $P$ offers a very simple but highly collateralized contract. It only accepted gold jewelry as collateral and approves all gold pawns, giving in exchange in cash the equivalent of 70\% of the weighted gold value. The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest. The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties. However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this by paying all accumulated interest). All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch. The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry. Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers. %This lets us focus more cleanly on behavioral economics aspects.

To study the benefits of private paternalism, we implemented a relatively large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total fee-inclusive financing cost. Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice? Notice that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees. Third, what types of clients would demand these contracts that restrict choice? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? A large and important lab experiment literature suggest that promises change behavior significantly in laboratory settings, but we know little about their effect on the field in natural environments.\footnote{Some important papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}). There is little information about them though.} Finally and importantly, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the commitment contract 
paternalistically?

The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{status-quo forcing group}). The second arm (\textit{fee-forcing group}) was given only a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.

We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.5\% on average, while the likelihood of recovering their pawn increases by 25.8\%. Results are robust to including in the cost definition transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings. The most economically vulnerable, those that report being stressed, and those that asked for a reminder at baseline, experience the largest financial cost savings. Those we classify as present biased and those that requested a reminder at baseline experience the largest effects on pawn recovery. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, we find that borrowers assigned to the forced fee-commitment contract are 5pp (55\% of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.

@@

In spite of these estimated benefits for all clients, their actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We had two ITAM students in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our ITAM assistants the loan differences. Furthermore take up is systematically predicted by baseline covariates, %\footnote{We find that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and ask for a remainder to payment (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice. The opposite holds for those that are more vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.}, 
making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large part of the literature of the literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. We estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.

@@

How much money is left on the table by the prevalence of the status-quo choice? We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \$238 pesos, close to 12\% of the average loan value. In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be welfare increasing for the overwhelming majority of clients.

Inspired by a significant lab experiment literature on the effects of promises on behavior, we also implemented a ``psychological commitment'' in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise. 
To do this we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and failed their word. Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise-forced} contract and the \textit{Status-quo} contract.

We document two main results in the promise arms. First, demand for the commitment-promise contract is three times bigger than for the commitment fee contract, with 31\% take-up. This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view. Second, the \textit{Promise-forcing} contract had zero effects on average and throughout the distribution on financing cost and pawn recovery. The same is true for the \textit{Promise-choice arm}. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior. This is true both imposed promises and chosen promises. Contrary to lab evidence, people did not keep the promise, at least the way it could be implemented in the field.

We contribute to several strands of literature. First, to the broad literature on commitment demand. A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}). We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial for almost everybody in our sample, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are \hl{400\%} higher as a fraction of the loan than those of \cite{John}.} Second, two recent papers show that among those who demand commitment, the extent of commitment needed is underestimated (\cite{Ted}, \cite{John}) and that subjects can hurt themselves by self-imposing too week a commitment. We contribute in design ---by not allowing choice of the extent of commitment--- but also on how we infer the underestimation of the value of commitment by subjects. While these two papers infer too low commitment from subjects failing to reach the goal ex-post, we infer it by quantifying forgone personalized treatment effects ex-ante. Third, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.

Fourth, we study \textit{both} causal effects and selection into frequent payment commitment loan contracts. \cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.} This paper fills part of this gap. \cite{Pande} study the effect of installment frequency on loan default and (surprisingly given their prevalence and the literature above) find null effects, while \cite{Murdoch} study selection into frequent payment microfinance loans, conjecturing that ``such repayment structure is potentially beneficial in fostering discipline among present-biased borrowers''. In contrast to \cite{Pande} we find very strong effects of payment frequency on decreased default.\footnote{Possibly because there are high levels of default in our context and not in theirs and because we have more statistical power from larger sample and individual randomization.} \cite{Murdoch}  show that a robust positive correlation exists between having present biased preferences in surveys and selecting into microfinance ---which they interpret as being due to the discipline of frequent payment--- acknowledging that the ``interpretation is suggestive... and needs to be confirmed by studies that establish causal links''. Our experimental test of this causal link rejects that people like and demand frequent payments (at least in our context). In contrast to \cite{Murdoch} we can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract. Fifth, we also contribute to the literature on the effect of promises by testing their effect on the field.

More importantly, our unique experimental design, paired with new machine learning methods to estimate heterogeneous treatment effects \cite{atheygrf}, allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment. In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}). Our context is one in which private paternalism (\cite{Laibson2018}) could work since almost all pawnshop clients would benefit from frequent payment contract yet there it almost no demand for them. After our experiment ended, Lender P started to tie in installment payment components to some of their contracts themselves.

@@

Pawn borrowing is one of the oldest form of borrowing and one to which people with little access to the formal credit market turn to for ``emergency'' loans. They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}). In spite of this, there are extremely few studies in the economics literature about it. Why people go, how much it costs, what different contracts can tell us about consumer biases. We study such  context with Lender $P$, one of the largest pawn shops in Mexico, with dozens of branches spanning multiple States in Mexico.

Lender $P$ was interested in understanding why half of their clients lost their pawn. It was concerned with high default rates for two reasons. The first is that the pawned piece may have a sentimental value to the client above of its gold value, making it inefficient for the lender to keep the piece. We actually find that clients report a subjective value that is almost twice the value of its gold content. Second, it thought that keeping the piece lowered client satisfaction and made the client less likely to return and pawn again. They were interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract. Default is really  in this context  compared to many papers in the microfinance literature. \cite{Pande} study of the effect of payment frequency work in a context where the rate of default is close to 1\%. %\cite{LittleAtAtime} has a baseline default of \hl{XX\%}.

One potential explanation for high default is that clients are really just selling their gold piece. This is unlikely for the large majority of people not only because the reported subjective value of the pawn is larger than the loan size for 86\% of them, but also because among those that lose their pawn 74\% paid a positive amount towards its recovery. This can only be rationalized if they expected to recover their pawn.  Figure \ref{proxy_naive} focuses on those that ended up losing the pawn in our experiment and plots different measures of engagement with Lender $P$. Panel (c) shows total payments that went towards the loan. On average clients that lost their pawn paid 34\% of the value of their loan. Panel (d) shows that while 40\% made zero payments, the rest made one or several payments. In fact, panel (b) shows that close to 55\% of clients extended the loan for another cycle and made payments in the second cycle.

@@

Lender $P$ had only one type of contract. It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime and no penalty for pre-payment. If the client paid the principal plus the accumulated interest before those 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments done. Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms. The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.

This contract was standard in the industry, the clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn. Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history. Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below, even though 90\% of them have pawned before.

@@

We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece. The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others. We were able to survey 7,704 clients (some refused). %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
The appendix \ref{baseline_survey} transcribes the questionnaire in English and presents summary stats. Survey response rate is 57\%, the Appendix Table \ref{balance_response} shows that response is not related to admin data observables.

@@

\subsection{More on implementation.} \label{implementation}
